$jk$-means tests

### 2016-09-26 Rmd/convergenceRatesBalancedLabels.Rmd
add balanced label test

###1. Generate Data
Let's generate data from 2 clusters, with size n/2, n/2*3

@@

mu0<- c(c(0.7), c(0.3))
mu<- matrix( 0,n*2,p)
mu[1:(n/2),]<- rep(c(0.7),each=(n/2))
mu[(n/2+1):(2*n),]<- rep(c(0.3),each=(n/2*3))

@@

functions to compute misclassification error and rmse of mean estimate:
NB: GMM can get stuck in saddle point at (w1=0, w2=1), so I removed the test result when it happened.
```{r}
computeMError<- function(jk, n,batchN){
  error<- numeric(batchN)
  for(b in 1:batchN){
    newOrder<- order(jk$mu[,1,b],decreasing = T)
    tM0<- c(0,1)[newOrder]
    trueM<- c(rep(tM0[1],(n/2)),rep(tM0[2],(n/2*3)))
    error[b]<- sum (jk$M[,b] != trueM) /2/n
    if( min(jk$w[,b])<0.1){
        error[b]<- NA
    }
  }
  error
}

@@

  save(result, file="resultRates.Rda")
}

@@

load("resultRates.Rda")

>>>>

###1. Generate Data
Let's generate data from 2 clusters, with size n, n

@@

mu0<- c(c(0.7), c(0.3))
mu<- matrix( 0,n*2,p)
mu[1:(n),]<- rep(c(0.7),each=(n))
mu[(n+1):(2*n),]<- rep(c(0.3),each=(n))

@@

functions to compute misclassification error and rmse of mean estimate:
NB: GMM can get stuck in saddle point at (w1=0, w2=1), so I removed the test result when it happened.
```{r}
computeMError<- function(jk, n,batchN){
  error<- numeric(batchN)
  for(b in 1:batchN){
    newOrder<- order(jk$mu[,1,b],decreasing = T)
    tM0<- c(0,1)[newOrder]
    trueM<- c(rep(tM0[1],(n)),rep(tM0[2],(n)))
    error[b]<- sum (jk$M[,b] != trueM) /2/n
    if( min(jk$w[,b])<0.1){
        error[b]<- NA
    }
  }
  error
}

@@

  save(result, file="resultRatesBalanced.Rda")
}

@@

load("resultRatesBalanced.Rda")
